A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Electron Beam Dynamics

### 2018-09-28 paper/theor-experiment.tex
updating exp tex

\begin{figure}%[h]
	\centering
	\includegraphics[width=\linewidth]{Report/timestep_comparison}
	\caption{Comparison of different fidelity models (dT stands for time step).}
	\label{tstep}
\end{figure}

@@

TITLE, STRING="ANL Optimisation";

@@

With the time steps and hyper parameters set by the work in Section \ref{awa:subsection:test}, 
the full optimization problem described in \ref{awaproblem} was run for 200 generations.
The initial number of individuals was fixed at 656, 
and the minimum number individuals in later generations was fixed at 328. 
These numbers were in part based on the architecture of the KNL's. 
Since each simulation takes 8 cores, and there are 64 cores per KNL node, 
we wanted a large population size that would fit evenly on these resources. 
Again, the location of optimization is $s_3=19.4$ [m].

\begin{figure}
	\includegraphics[width=0.5\textwidth]{../pareto_stat_plots/xy_vs_pxy_pareto_front_quads_before_Q5}
	\caption{Pareto front comparing transverse beam sizes ($\sigma_{x,y}$) and transverse momentum ($\sigma_{px,py}$).}
	\label{fig:pareto1}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/dE_vs_zrms_pareto_front_quads_before_Q5_zoomout}%
	\llap{\raisebox{1.9cm}{%  move next graphics to top right corner
			\includegraphics[height=4.5cm]{../pareto_stat_plots/dE_vs_zrms_pareto_front_quads_before_Q5}%
	}}
	\caption{Pareto front comparing energy spread (dE) and bunch length ($\sigma_z$). \nrnote{add tikz arrows to point to left side of curve?}}
	\label{fig:pareto2}
\end{figure}

@@

With these observations in mind, several beam parameters corresponding to
options on the Pareto Front in Fig.~\ref{fig:pareto1} were plotted and compared. 
A select result is shown in Fig.~\ref{fig:stat}.  \lsedit{It would be a nice addition to say which point on the pareto front that was, perhaps marking it on the curve}
The maximum beam sizes are well below the beam pipe aperture limits as shown in Fig.~\ref{fig:stat} (b).
The solution is nearly round, which will increase changes of keeping the beam nearly round
as it travels to the last triplet in Fig.~\ref{awa-tba}.
Overall this solution is satisfactory, and meets all requirements at the AWA.

\begin{figure}
	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/xy-max-min-zrms_newobj}
	\caption{Optimized beam sizes along high charge beam line. The gun is located at $s=0$, 
	both x and y beam sizes are shown. The black line represents the relevant beam line aperture, while
	the green line indicates the location of the optimisation.}
	\label{fig:stat}
\end{figure}

>>>>

\begin{figure}%[h]
	\centering
	\includegraphics[width=\linewidth]{Report/timestep_comparison_paper}
	\caption{Comparison of different fidelity models (dT stands for time step).}
	\label{tstep}
\end{figure}

@@

TITLE, STRING="ANL Optimization";

@@

With the time steps and hyper parameters set by the work in Section \ref{awa:subsection:test}, 
the full optimization problem described in \ref{awaproblem} was run for 200 generations.
The initial number of individuals was fixed at 656, 
and the minimum number individuals in later generations was fixed at 328. 
These numbers were in part based on the architecture of the KNL's. 
Since each simulation takes 8 cores, and there are 64 cores per KNL node, 
we wanted a large population size that would fit evenly on these resources. 
Again, the location of optimization is $s_3=19.4$ [m]. 
\begin{figure}
	\begin{center}		
		\begin{tikzpicture}[scale=1]
		\node (fig1) at (0,0)
		{\includegraphics[width=0.5\textwidth]{../pareto_stat_plots/xy_vs_pxy_pareto_front_quads_before_Q5}};
		\node[star, star points=5, star point ratio=0.5, fill=yellow, draw](key) at (3.35,-1.7) {};
		\end{tikzpicture}
	\end{center} 
		\caption{Pareto front comparing transverse beam sizes ($\sigma_{x,y}$) and transverse momentum ($\sigma_{px,py}$). The yellow star indicates the 
		point plotted in Fig.~\ref{fig:stat}}
	\label{fig:pareto1}
\end{figure}

\iffalse
\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/dE_vs_zrms_pareto_front_quads_before_Q5_zoomout}%
	\llap{\raisebox{1.9cm}{%  move next graphics to top right corner
			\includegraphics[height=4.5cm]{../pareto_stat_plots/dE_vs_zrms_pareto_front_quads_before_Q5}%
	}}
	\caption{Pareto front comparing energy spread (dE) and bunch length ($\sigma_z$). \nrnote{add tikz arrows to point to left side of curve?}}
	\label{fig:pareto2}
\end{figure}  
\fi

@@

With these observations in mind, several beam parameters corresponding to
options on the Pareto Front in Fig.~\ref{fig:pareto1} were plotted and compared. 
A select result is shown in Fig.~\ref{fig:stat}.  
The maximum beam sizes are well below the beam pipe aperture limits as shown in Fig.~\ref{fig:stat} (b).
The solution is nearly round, which will increase changes of keeping the beam nearly round
as it travels to the last triplet in Fig.~\ref{awa-tba}.
Overall this solution is satisfactory, and meets all requirements at the AWA.

\begin{figure}
	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/xy-max-min-sigma-paper}
	\caption{Optimized beam sizes along high charge beam line. The gun is located at $s=0$, 
	both x and y beam sizes are shown. The black line represents the relevant beam line aperture, while
	the green line indicates the location of the optimization.}
	\label{fig:stat}
\end{figure}
\begin{table}%[h!]
	\begin{center}
		\caption{Input Parameters for large scale TBA optimization runs.}
		\label{tab:designopt}   
		\begin{tabular}{l|c|c}
			\noalign{\smallskip}\hline\noalign{\smallskip}
			%\rowcolor{blue!30} 
			\textbf{Design Variable} & \textbf{Unit}	&  \textbf{Value}  \\ 
			\noalign{\smallskip}\hline\noalign{\smallskip}
			{Buck Focusing Solenoid} & amps	& 478 \\
			Matching Solenoid &	amps	& 197	  \\
			Quadrupole 1& T-m		& -0.8	\\ 
			Quadrupole 2& T-m		& 0.9	\\
			Quadrupole 3 & T-m		& 0.8	\\
			Quadrupole 4 & T-m		& -1.0	\\ 
			Bunch Length & mm 		& 1.5	\\
			\noalign{\smallskip}\hline\noalign{\smallskip}
		\end{tabular}
	\end{center}
\end{table}
